### 2023-11-07 main.tex
''

In this section we aim to use duality and the matrix product ansatz (MPA) to determine the moments and correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}. As it will turn out, the commutation relations of the matrix product ansatz allowing to determine a closed formula for all correlations. As a by-product, absorption probabilities can be explicitly found.%, giving a further probabilistic interpretation for the non-equilibrium steady state. 

@@

The matrix product ansatz has been formulated in \cite{vanicat2017exact}, here we briefly recall it.

@@

 where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} become simpler. As a consequence, the steady state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly. Finally, reversing the transformations we retrieve $|\Psi\rangle$.

 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. \\

@@

 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$. In each of these points there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$. Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by

@@

The absorption probabilities are given by  

@@

	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformation that bring the original Hamiltonian $H$ to $H^{'}$ and $H^{''}$, with triangular and triangular diagonal boundaries respectively. Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively. 

@@

	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state using $|\Psi^{'}\rangle$ of the previous step. Exploiting duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$. However, for the sake of completeness we report it Appendix \ref{appB}. 

@@

We introduce
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
that is composed by a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
Therefore, by taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{left}^{''}+H_{bulk}+H_{right}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ reads
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$ and $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
\begin{comment}
 We compute
\begin{enumerate}
	\item $A_{N}=e_{aN}$ with $a\neq 1$
	\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
	\end{equation}
\item $A_{a}=e_{aa}$ with $a\neq 1$
\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
	\end{equation}
Indeed 
\begin{equation}
	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
\end{equation}
\end{enumerate}
\end{comment}
Therefore, using \eqref{HT-BA} we obtain for the left boundary 
\begin{equation}
	\begin{split}
		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}
% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
		=
		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
		=
		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
	\end{split}
\end{equation}
Similarly, using again \eqref{HT-BA} we have for the right boundary 
\begin{equation}
	\begin{split}
% <<<<<<< HEAD
% 			H_{right}^{''}&=S_{2}H_{right}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
% 			\\&=
% =======
			H_{right}^{''}=S_{2}H_{right}^{'}S_{2}^{-1}
% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
			=
% >>>>>>> c7f11c8ce72f62a51dea6d275334057112d03a47
			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
			e_{NN}^{L}-\mathbbm{1}\dt
	\end{split}
\end{equation}
The relation between eigenvectors with vanishing eigenvalue is 
\begin{equation}\label{S2-Inverse}
	|\Psi^{'}\rangle = S_{2}^{-1}|\Psi^{''}\rangle
\end{equation}
and $|\Psi^{''}\rangle$ solves
\begin{equation}\label{steadyS-SECOND-def}
	H^{''}|\Psi^{''}\rangle=0\dt
\end{equation}
It is convenient to introduce also the transformation
\begin{equation}\label{similarity}
	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
\end{equation}
This matrix $S$ connects $H$ with $H^{''}$ by 
\begin{equation}
H=S^{-1}H^{''}S
\end{equation}
and, the relation between eigenvectors with vanishing eigenvalue is
\begin{equation}
	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle\dt
\end{equation}

@@

This notation is equivalent to the one introduced. Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$. Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$. With this notation, we have that 
\begin{equation}\label{notation}
	|n^{x}\rangle =|\tau_{x}\rangle \qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
\end{equation}
with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$.
\end{comment} 
We state the following result: the ground state of the Hamiltonian $H^{''}$ is given by 
\begin{equation}\label{ResulsBasis}
	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
\end{equation}
%\begin{equation}\label{ResulsBasis}
%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
%\end{equation}
where 
\begin{equation}
    \delta_{\tau_{x},N}:=\begin{cases}
        N\quad \text{if}\quad \tau_{x}=N\\
        0\quad \text{otherwise}
    \end{cases}
\end{equation}

@@

For the sake of notation 

@@

and, we can also reverse the transformation by $S^{-1}$ and get back: 

@@

with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$, see \eqref{Xtildes2b}. 

@@

	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+\lambda_{\tau_{x}}\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{n_{a}^{x}}\dt

@@

Therefore, we write the coefficients of the linear combination \eqref{toDetermineTilde} as 

@@

\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain. Using the exponential series, the matrix $\mathcal{S}_{2}$ is given by 

@@

The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
To find these quantities we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$. Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
\begin{equation}
	\begin{split}
\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
  \\&+
  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}}
	\end{split}
\end{equation}
\end{comment}
%Now we can write the ground state of $H^{''}$ as \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients $\psi^{''}(\bm{\mu})$ are given in \eqref{coefficients-psiSec}.
%Therefore, we have that equation \eqref{ABS_intermediate} becomes
%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads

@@

We aim to compute

@@

Therefore, we have that 

@@

The computations made for the multi-species stirring process can be specialized for the colour-blind case $N=2$, i.e. when only one type of non-empty particle is considered. In this situation we retrieve the SSEP, already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations. 

@@

 In case of $N=2$ we stop distinguishing the types of (non-empty) particles and we retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}:  

@@

\textbf{Proof:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$. There are many values of $c$'s that give the same $q$, therefore we define $q$ labels for the $c$'s equal to $1$ denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ and such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$, i.e. $c_{x_{\ell_{i}}}=1$ for $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$. Therefore, we have 

@@

Varying all possible $c$'s in \eqref{exactCorrelations} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain that 

@@

We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. Thus, arguing as in \eqref{remove-exponent} and using \eqref{Gamma-product} we have that 

@@

	\prod_{x=1}^{L}\left(L+2-x-\sum_{j=x}^{L}c_{j}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)\dt

>>>>

In this section we aim to use duality and the matrix product ansatz (MPA) to determine the moments and correlations of the non-equilibrium steady state for the integrable version of the multi-species stirring process, defined in Subsection \ref{integrableChain-duality}. As it will turn out, the commutation relations of the matrix product ansatz allows to determine a closed formula for all correlations. As a by-product, absorption probabilities can be explicitly found.%, giving a further probabilistic interpretation for the non-equilibrium steady state. 

@@

The matrix product ansatz for the multi-species stirring process has been formulated in \cite{vanicat2017exact}, here we briefly recall the main steps.

@@

 where $H^{'}= S_{1} H S_{1}^{-1} $ has both boundary terms in a triangular form, and $H^{''} = S_{2}H' S_{2}^{-1}$ has the left boundary in a triangular form and the right boundary is diagonal. Using these transformations the commutators \eqref{bulk} and the action on the boundary vectors \eqref{leftBoundary}, \eqref{rightBoundary} become simpler. As a consequence, the ground state $|\Psi^{''}\rangle$ of $H^{''}$ can be written explicitly. Finally, reversing the transformations we retrieve $|\Psi\rangle$.

 The first transformation $S_{1}$ is closely related to the duality matrix and we will see that $H^{'}$ is $\widetilde{H}^{T}$, up to the extra-site term described by the bosonic creation operator in \eqref{siteDualHamiltonian}. Therefore, $H^{'}$ is not stochastic. The second transformation $S_{2}$ diagonalizes the right boundary. Finally, the composition  $S_{2} S_{1}$ allows to simplify the commutators of the MPA algebra. 

@@

 Consider $m\in \{1,\ldots,L\}$ points with coordinates given by $(x_{1},\ldots,x_{m})$, such that $x_{k}<x_{k+1}$ $\forall k\in \{1,\ldots,m-1\}$. In each of these points we assume that there is a particle of species $a_{k}\in \{1,\ldots,N-1\}$. Then, with respect to the non-equilibrium stationary distribution, the correlations among these particles are given by

@@

Knowing the non-equilibrium steady state correlations, we can read-off the absorption probabilities defined in \eqref{absProbabilitiesIntegrable}. They are given by

@@

	\item In Subsection \ref{subsectionSTransf}, we introduce two similarity transformation that bring the original Hamiltonian $H$ to $H^{'}$ and $H^{''}$, with triangular and triangular-diagonal boundaries respectively. Associated to $H^{'}$ and $H^{''}$ there are two ground states denoted by $|\Psi^{'}\rangle$ and $|\Psi^{''}\rangle$ respectively. 

@@

	\item In Subsection \ref{subsection-exact} we compute the non-equilibrium steady state correlations using $|\Psi^{'}\rangle$ of the previous step. Exploiting duality to compute these correlation, we do not need the explicit expression of the steady state $|\Psi\rangle$. However, for the sake of completeness we report $|\Psi\rangle$ in Appendix \ref{appB}. 

@@

We introduce
 \begin{equation}
 	\mathcal{S}_{2}^{x}:=\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\co%=\mathbbm{1}-\sum_{a=2}^{N}\beta_{a}e_{a1}
 \end{equation}
that is composed by a copy of $\mathcal{S}_{2}$ (see \eqref{S2Gen}) acting at site $x$ and with identities acting at all other sites of the chain. 
Therefore, by taking the product over the chain we obtain 
\begin{equation}\label{S2-Whole}
	S_{2}=\prod_{x=1}^{L}\mathcal{S}_{2}^{x}\dt
\end{equation}
We define 
\begin{equation}\label{HSecond}
	H^{''}=H_{left}^{''}+H_{bulk}+H_{right}^{''}\co
\end{equation}
that is related to $H'$ by
\begin{equation}
	H^{''}=S_{2}H^{'}S_{2}^{-1}\dt
\end{equation}
The boundary Hamiltonians of $H^{''}$ reads
\begin{align}\label{tri-diag-boundaryHamiltonians}
	H_{left}^{''}=e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\qquad H_{right}^{''}=e_{NN}^{L}-\mathbbm{1}\dt
\end{align}
The left one is lower triangular and depends on the differences between the boundary parameters, while the right one is diagonal. Equations \eqref{tri-diag-boundaryHamiltonians} are proved using the Hadamard formula \eqref{HadamardFormula} with $B=\sum_{c=1}^{N-1}\beta_{c}e_{cN}$, $A_{N}=e_{aN},$ and $A_{a}=e_{aa}$.
\begin{comment}
 We compute
\begin{enumerate}
	\item $A_{N}=e_{aN}$ with $a\neq 1$
	\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aN}\exp{\left(\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}=e_{aN}
	\end{equation}
\item $A_{a}=e_{aa}$ with $a\neq 1$
\begin{equation}
		\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}\right)}e_{aa}\exp{\left(\sum_{c=1}^{N}\beta_{c}e_{cN}\right)}=e_{aa}+\beta_{a}e_{aN}
	\end{equation}
Indeed 
\begin{equation}
	\sum_{c=1}^{N-1}[e_{cN},e_{aa}]=\sum_{c=1}^{N-1}\beta_{c}\left(e_{ca}\delta_{aN}-e_{aN}\delta_{ca}\right)=-\beta_{a}e_{aN}
\end{equation}
\end{enumerate}
\end{comment}
Therefore, using \eqref{HT-BA} we obtain for the left boundary 
\begin{equation}
	\begin{split}
		H_{left}^{''}&=S_{2}H_{left}^{'}S_{2}^{-1}
% 		=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{1}\right)}
		=
		\sum_{a=1}^{N-1}\left(\alpha_{a}e_{aN}^{1}-e_{aa}^{1}-\beta_{a}e_{aN}^{1}\right)
		=
		e_{NN}^{1}-\mathbbm{1}+\sum_{a=1}^{N-1}(\alpha_{a}-\beta_{a})e_{aN}^{1}\dt
	\end{split}
\end{equation}
Similarly, using again \eqref{HT-BA} we have for the right boundary 
\begin{equation}
	\begin{split}
% <<<<<<< HEAD
% 			H_{right}^{''}&=S_{2}H_{right}^{'}S_{2}^{-1}=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
% 			\\&=
% =======
			H_{right}^{''}=S_{2}H_{right}^{'}S_{2}^{-1}
% 			&=\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}\right)\exp{\left(-\sum_{c=1}^{N-1}\beta_{c}e_{cN}^{L}\right)}
			=
% >>>>>>> c7f11c8ce72f62a51dea6d275334057112d03a47
			\sum_{a=1}^{N-1}\left(\beta_{a}e_{aN}^{L}-e_{aa}^{L}-\beta_{a}e_{aN}^{L}\right)=
			e_{NN}^{L}-\mathbbm{1}\dt
	\end{split}
\end{equation}
The relation between eigenvectors with vanishing eigenvalue is 
\begin{equation}\label{S2-Inverse}
	|\Psi^{'}\rangle = S_{2}^{-1}|\Psi^{''}\rangle
\end{equation}
and $|\Psi^{''}\rangle$ solves
\begin{equation}\label{steadyS-SECOND-def}
	H^{''}|\Psi^{''}\rangle=0\dt
\end{equation}
It is convenient to introduce also the transformation
\begin{equation}\label{similarity}
	S=S_{2}S_{1}=\prod_{x=1}^{L}\exp{\left(-\sum_{a=1}^{N-1}\beta_{a}e_{aN}^{x}\right)}\exp{\left(\sum_{a=1}^{N-1}e_{aN}^{x}\right)}\dt
\end{equation}
This matrix $S$ connects $H$ with $H^{''}$ by 
\begin{equation}
H=S^{-1}H^{''}S
\end{equation}
and, the relation between eigenvectors with vanishing eigenvalue is
\begin{equation}
	|\Psi\rangle=S^{-1}|\Psi^{''}\rangle\dt
\end{equation}

@@

This notation is equivalent to the one introduced. Indeed, assume that at site $x$ we have a particle of type $a\in\{1,\ldots,N\} $, then $|n^{x}\rangle$ is composed by zeros but in the component $n_{a}^{x}$ where there is $1$. Therefore, we can uniquely associate  $\tau_{x}=a$ to this $|n^{x}\rangle$, denoting the presence of the species $a$ at site $x$. With this notation, we have that 
\begin{equation}\label{notation}
	|n^{x}\rangle =|\tau_{x}\rangle \qquad \text{and}\qquad|\bm{n}\rangle=|\bm{\tau}\rangle
\end{equation}
with the meaning explained above. It will be useful to introduce also $\bm{\tau}=(\tau_{x})_{x\in \{1,\ldots,L\}}$.
\end{comment} 
The ground state of the Hamiltonian $H^{''}$ is given by 
\begin{equation}\label{ResulsBasis}
	|\Psi^{''} \rangle= \sum_{\bm{\tau}\in \Omega}\frac{1}{\left(1+L\right)!}\prod_{x=1}^{L} \lambda_{\tau_{x}}^{(1-\delta_{\tau_{x},N})}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right) |\bm{\tau}\rangle
\end{equation}
%\begin{equation}\label{ResulsBasis}
%	|\Psi^{''} \rangle=\sum_{\tau_{1},\ldots,\tau_{L}=1}^{N}\frac{\Gamma\left(2+\sum_{x=1}^{L}\delta_{\tau_{x},N}\right)}{\Gamma\left(2+L\right)}\left(\prod_{x=1}^{L}\left[\lambda_{\tau_{x}}\left(1+\sum_{j=x}^{L}\delta_{\tau_{j},N}\right)\right]^{1-\delta_{\tau_{x},N}}\right)|\mathbf{\bm{\tau}}\rangle
%\end{equation}
where 
\begin{equation}
    \delta_{\tau_{x},N}:=\begin{cases}
        N\quad \text{if}\quad \tau_{x}=N\\
        0\quad \text{otherwise}
    \end{cases}
\end{equation}

@@

For the sake of notation we denote by

@@

We can also reverse the transformation by $S^{-1}$ and get back: 

@@

with $\widetilde{X}_{N}=\widetilde{X}_{1}+\ldots+\widetilde{X}_{N}$. 

@@

	\prod_{x=1}^{L}\widetilde{X}_{\tau_{x}}=\widetilde{X}_{N}^{\sum_{x=1}^{L}\delta_{\tau_{x},N}}\prod_{x=1}^{L}\left(\widetilde{X}_{\tau_{x}}+\lambda_{\tau_{x}}\sum_{j=x}^{L}\delta_{\tau_{x},N}\right)^{1-\delta_{\tau_{x},N}}\dt

@@

Therefore, we write

@@

\paragraph{Proof of formula \eqref{ABS-vect}} We have that $|\Psi^{'}\rangle=S_{2}^{-1}|\Psi^{''}\rangle$ (see \eqref{S2-Inverse}), thus we only need to show how the transformation $S_{2}^{-1}$ acts on the vector $|\Psi^{''}\rangle$. Here it is more convenient to consider the matrix $\mathcal{S}_{2}^{-1}$ defined in \eqref{S2Gen}, acting on a single site, and then make explicitly the tensor product over the chain. Using the exponential series we have that  

@@

The product $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}|\Psi^{''}\rangle$ gives a vector $|\Psi^{'}\rangle$ whose component are denoted by $\Psi^{'}(\bm{\tau})$. 
To find these quantities we need to fix the rows correspondent to $\bm{\tau}$ in the matrix $\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}$. Consider a string $\bm{\tau}=(\tau_{1},\ldots,\tau_{L})$ with $\tau_{1},\ldots,\tau_{L}\in \{1,\ldots,N\}$, then the corresponding row reads
\left(\mathcal{S}_{2}^{-1}\right)^{\otimes L}_{\bm{\tau}}&=\,e_{\tau_{1},\ldots,\tau_{L}}^{\tau_{1},\ldots,\tau_{L}}+\sum_{q_{1}=1}^{L}(1-\delta_{\tau_{q_{1}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{1},\ldots,\varphi_{L}^{1}}\beta_{\tau_{q_{1}}}\\&+\sum_{q_{1},q_{2}=1\,:\,q_{1}\neq q_{2}}^{L}(1-\delta_{\tau_{q_{1}},N})(1-\delta_{\tau_{q_{2}},N})e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{2},\ldots,\varphi_{L}^{2}}\beta_{\tau_{q_{1}}}\beta_{\tau_{q_{2}}}
  \ldots+\sum_{q_{1},\ldots,q_{L}=1\,:\,q_{i}\neq q_{j}\;\text{if}\;i\neq j}^{L}\left(\prod_{x=1}^{L}(1-\delta_{\tau_{x},N})\right)\left(\beta_{\tau_{x}}\right)^{1-\delta_{\tau_{x},1}}e_{\tau_{1},\ldots,\tau_{L}}^{\varphi_{1}^{L},\ldots,\varphi_{L}^{L}}
%Now we can write the ground state of $H^{''}$ as \begin{equation}|\Psi^{''}\rangle=\sum_{\mu_{1},\ldots,\mu_{L}=1}^{N}\Psi^{''}(\bm{\mu})|\bm{\mu}\rangle\end{equation} with the coefficients $\psi^{''}(\bm{\mu})$ are given in \eqref{coefficients-psiSec}.
%Therefore, we have that equation \eqref{ABS_intermediate} becomes
%Because of the exponent $(1-\delta_{\tau_{x},1})$, the element $\Psi^{''}(\bm{\tau})$ has, up the term $\frac{\Gamma(2+\sum_{i=1}^{L}\delta_{\tau_{x},1})}{\Gamma(L+2)}$, a contribution of a factor $\lambda_{\tau_{x}}\left(2+L-x-\sum_{j=x}^{L}(1-\delta_{\tau_{x},1})\right)$ if the site is non empty, and a contribution of a factor "$1$" if the site is empty, it is convenient to introduce the $c_{i}$ of defined in \eqref{CiEquation}. Then, equation  \eqref{ABS_intermediate} reads 

@@

We consider $m\in \{1,\ldots,L\}$ sites with coordinates $x_{1},\ldots,x_{m}\in \{1,\ldots,L\}$ such that $x_{k}<x_{k+1}$ for all $k\in \{1,\ldots,m-1\}$. Each of these sites is occupied by $a_{k}\in\{1,\ldots,N-1\}$, we aim to compute

@@

Therefore, it follows that 

@@

The computations made for the multi-species stirring process can be specialized for the colour-blind case $N=2$, i.e. when only one type of non-empty particle is considered. In this situation we retrieve the SSEP, that was already solved with the quantum inverse scattering method in \cite{frassek2020eigenstates}. We report the Hamiltonians and the similarity transformations of SEEP: 

@@

We retrieve the closed formula for correlations in the non-equilibrium steady state found in \cite[(4.26)]{frassek2020eigenstates}:  

@@

\textbf{Proof:} Starting from \eqref{exactCorrelations} we exploit indistinguishability of particles and we introduce $q=\sum_{k=1}^{m}c_{x_{k}}$. There are many values of $c$'s that give the same $q$, therefore we define $q$ labels denoted by $\ell_{1},\ldots,\ell_{q}\in \{1,\ldots,m\}$ such that  $\ell_{1}<\ell_{2}<\ldots<\ell_{q}$. These labels are defined in order to $x_{\ell_{1}},\ldots,x_{\ell_{q}}\in\{x_{1},\dots,x_{m}\}$ are such that $c_{x{\ell_{k}}}=1$ for all $k\in \{1,\ldots,q\}$ and $c_{x}=0$ for $x\notin \{x_{\ell_{1}},\ldots,x_{\ell_{q}}\}$. Therefore, we have 

@@

Varying all possible $c$'s in \eqref{exactCorrelations} is equivalent of varying all possible $q$ and all possible $\ell_{1},\ldots,\ell_{q}$, therefore we obtain 

@@

We introduce $q=\sum_{x=1}^{L}\delta_{\tau_{x},1}$. Moreover, for each $q\in \{1,\ldots,L\}$ we call $1\leq\ell_{1}<\ldots,\ell_{q}\leq L$ the coordinates where particles of type $1$ are present. Thus, arguing as before and using \eqref{Gamma-product} we have that 

@@

	\prod_{x=1}^{L}\left(L+2-x-\sum_{j=x}^{L}c_{j}\right)^{c_{x}}=\prod_{k=1}^{q}\left(L+2-x_{\ell_{k}}-\sum_{j=x_{\ell_{k}}}^{L}c_{j}\right)=\prod_{k=1}^{q}\left(1+L-x_{\ell_{k}}-q+k\right)\dt
